\section{Introduction}
In late 2017, \gls{redditor} \textit{deepfake} began publishing pornographic footage
on \url{https://www.reddit.com/r/deepfakes}, where he replaced the actors' faces
with those of celebrities --- without their consent. As a consequence, he
received increased media coverage in early 2018, after the release of a first 
article and interview on vice-motherboard~\cite{Cole.2017}. While he coined the
term \textit{DeepFake} for face-\textit{replacement} and face-\textit{reenactment}
technologies, both were already actively researched in academia with research 
dating back to at least 1997~\cite{Bregler.1997}.
Following this, there was an increased awareness for \textit{DeepFakes} which also
caused more research to be conducted, from \(3\) papers published in \(2017\) to
more than \(150\) in \(2018-2019\)~\cite{mirsky_creation_2020} as well as
resulting in first government action~\cite{senate_-_homeland_security_and_governmental_affairs__house_-_energy_and_commerce_deepfake_2019}.

\par
The aim of this paper is
\begin{enumerate*}[a.)]
    \item to give the reader an introduction to the process of creating manipulated
    images via the generic content manipulation technique named \textit{DeepFake}
    and
    \item to give an overview on different approaches to the detection of such manipulated footage.
\end{enumerate*}

\subsection{Structure}
In the remainder of this section, the limitations to the scope of this paper are
presented. Then, in \cref{sect:background}, an overview and definition of \textit{DeepFakes}
is given, including also a discussion of ethical challenges.
This is followed by a summary of the creation of many-to-many \textit{DeepFakes}
in \cref{sect:creation-of-deepfakes}. Finally, different methods of detecting
\textit{DeepFakes} can be found in \cref{sect:detection}.

\subsection{Limitations}\label{subsect:limitations}
While there are multiple \textit{flavors} of \textit{DeepFakes} (see \cref{subsubsect:deepfake-flavors}),
this study explicitly works within the scope of many-to-many mimical puppetry and its
detection. This means that neither \textit{DeepFakes} of text or audio signals,
face-replacement or body reenactment are part of this work. This is mainly
due to spatial constraints and considering that in their core principles the techniques are mostly
similar. Beyond that, one-to-one and one-to-many \textit{DeepFakes} (see \cref{subsubsect:generalizability-deepfakes})
are not examined. This restriction is made because we consider many-to-many \textit{DeepFakes}
to be of greater risk due to their more generic nature and thus larger applicability.
\todo{unify all the sources, no duplications}